Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-13 articles/cycle/alps-cycle.tex
Fix two bugs in internal references.

    Although the palaeo-climate forcing was adapted (Sect.~\label{sec:climate})
    to model this maximum configuration in broad agreement with the geological
    reconstruction of the LGM extent (Fig.~\ref{fig:lgmvel}a, solid red line),
    local discrepancies remain. Most notably, reconstructed ice extent in the
    north-western Alps, including the Rhone Glacier complex, the Jura ice cap,
    and the Lyon Lobe, is largely missing from our model results. On the other
    hand, the model yields excessive glaciation in the eastern Alps, where the
    Palten, Drau and Sava glaciers are modelled to extend tens of kilometers
    beyond the mapped moraines. These discrepancies might indicate that the
    LGM climate was characterized by an east-west gradient in temperature or
    precipitation anomalies relative to present not included in the climate
    forcing, or perhaps a east-west gradient in variables not accounted for
    by the PDD model, such as cloud cover or dust deposition.

    On a more regional level, the modelled maximum extent of the Ticino, Iseo,
    Garda and Piave glaciers in the central southern Alps is constrained
    several kilometres within the mapped LGM moraines. This appears to result
    from the paleo-precipitation reduction used to force the model
    (Fig.~\ref{footprints}b), which is likely unrealistic in at least this part
    of the model domain. On the other hand, the Durance glacier in the
    south-western Alps is modelled to extend several kilometers beyond the
    mapped limit, indicating that the LGM temperature depression was likely
    dampened by Mediterranean climate in this part of the model domain.

>>>>

    Although the palaeo-climate forcing was adapted (Sect.~\ref{sec:climate})
    to model this maximum configuration in broad agreement with the geological
    reconstruction of the LGM extent (Fig.~\ref{fig:lgmvel}a, solid red line),
    local discrepancies remain. Most notably, reconstructed ice extent in the
    north-western Alps, including the Rhone Glacier complex, the Jura ice cap,
    and the Lyon Lobe, is largely missing from our model results. On the other
    hand, the model yields excessive glaciation in the eastern Alps, where the
    Palten, Drau and Sava glaciers are modelled to extend tens of kilometers
    beyond the mapped moraines. These discrepancies might indicate that the
    LGM climate was characterized by an east-west gradient in temperature or
    precipitation anomalies relative to present not included in the climate
    forcing, or perhaps a east-west gradient in variables not accounted for
    by the PDD model, such as cloud cover or dust deposition.

    On a more regional level, the modelled maximum extent of the Ticino, Iseo,
    Garda and Piave glaciers in the central southern Alps is constrained
    several kilometres within the mapped LGM moraines. This appears to result
    from the paleo-precipitation reduction used to force the model
    (Fig.~\ref{fig:footprints}b), which is likely unrealistic in at least this
    part of the model domain. On the other hand, the Durance glacier in the
    south-western Alps is modelled to extend several kilometers beyond the
    mapped limit, indicating that the LGM temperature depression was likely
    dampened by Mediterranean climate in this part of the model domain.
